---
title: "Constructing Custom Examples"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 6
vignette: >
  %\VignetteIndexEntry{Constructing Custom Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction

This vignette serves as a primer to help construct detailed, coherent and consistent 
Examples Sections in function documentation using the custom `rdx_roclet()` 
functionality - please see `demo_fun()` for a dummy example and  [`derive_extreme_records.R` in admiral](https://github.com/pharmaverse/admiral/blob/main/R/derive_extreme_records.R) 
for an example of this in action. 

In practice, the rules and directives shown below cannot always be applied to the 
letter, because each function and its context are different and may have varying 
requirements. As such, developers are encouraged to treat these directives 
heuristically and always apply their judgement when constructing Examples Sections.

# How to use the `@caption`, `@info` and `@code` tags together in a "block"

The Examples Section should consist of a series of example blocks, usually made up 
of one call each to `@caption`, `@info` and `@code`. See the example below:

```{r, eval = FALSE}
#' @examplesx
#' 
#' @caption Showcasing the first functionality of `fun()` (`arg1`)
#' 
#' @info This is the detailed text for the first example.
#' 
#' @code
#' 
#' fun(arg1 = TRUE)
#' 
#' @caption Showcasing the second functionality of `fun()` (`arg2`)
#' 
#' @info This is the detailed text for the first example.
#' 
#' @code
#' 
#' fun(arg2 = FALSE)
```

Within each block:

- The `@caption` tag should be used to provide a brief description of the example. 
This is the text which will show up in the table of contents on the right hand 
side of the function documentation. If possible and/or relevant, the text should
specify which argument(s) are being showcased in that example. 
- The `@info` tag should be used to provide a more detailed description of the
example. If relevant, it should contain some context behind the example (i.e. 
__why__ this may be a relevant scenario to consider). 
- The `@code` tag should be used to provide the code for the example. The code 
should be as self-contained as possible. The dataset/object being created should
be printed at the end of the section.

Note that a more complex block may also have multiple `@info` and`@code` 
sections after the `@caption` if it is particularly involved.

# How to sequence your blocks

Successive example blocks should build in complexity. The first examples should
showcase the most "minimal" execution of the function, with only the required
arguments being triggered and the default values discussed. The data in 
these examples is as concise as possible and may not be ADaM compliant, e.g.,
`STUDYID` may not be included or `AVISITN` may be present without `AVISIT`.

Later blocks should then bring in one/a few more arguments at a time as the
use-case becomes more involved. If possible, they should build on top of 
earlier blocks (i.e. use the same data but changing the scope of the function
call to add complexity), but if this is not possible, then new scenarios 
can be considered.

All example blocks should answer questions like "what does this function do?"
or "how does this argument work?".
  
# Data sections

If all examples can be run on the same/similar data, you may wish to (optionally)
include a "Data setup" block at the start of the Examples Section to create the 
dummy dataset(s) that can then be used in each block. Please see
[derive_summary_records()](https://pharmaverse.github.io/admiral/main/reference/derive_summary_records.html#examples)
as an example.
